\subsection{Data Insertion}\label{sec:DataInsertion}

Data insertion are the actions that will fill the supply chain flow with data. Once a new supply chain is created by the admin user, it is ready to be populated with information. Member and admin users are responsible for perform these actions. In Data Insertion phase users can update information from a specific step and substep and move assets depending on the rules applied in the setup phase.

\subsubsection{Raw material/Producer}\label{sec:Rawmaterial}
Providers of raw materials, the quarrier or miner, a gravel producing company. Responsible for the extraction of raw materials (natural resources) and how they are firstly processed (pre-processed) by the suppliers or vendors in order to be delivered to the next stage.

\subsubsection{Manufacturer}\label{sec:Manufacturer}
The same as raw material/producer for gravel, or a machinery/equipment producer. Responsible for the process of converting the raw materials into products that are ready to sell.

\subsubsection{Distributor}\label{sec:Distributor}
Building materials shop or distributor. This actor is responsible of moving the output of the manufacturer (e.g., the product) from manufacturer’s site to a wholesaler and/or retailers.

\subsubsection{Wholesaler}\label{sec:Wholesaler}
Seller of gravel in large quantities, generally to businesses like building companies. Wholesalers in general do not sell products directly to the public, but to other retailers instead.

\subsubsection{Retailer}\label{sec:Retailer}
Seller of gravel in small quantities, generally to natural persons.